%-------------------------
% Resume in Latex
% Author : Ajay G
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\usepackage[svgnames]{xcolor} % Use 'svgnames' for a wider range of color names
\usepackage{hyperref}

% --- Hyperlink Setup ---
\hypersetup{
    colorlinks=true, 
    linktoc=all,     
    urlcolor=LightSlateGray,
}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Ajay Gopi} \\ \vspace{1pt}
    \small (+1) 585 498 8027 $|$ \href{mailto:ajaynaidu96@outlook.com}{\underline{Email}} $|$ 
    \href{https://www.linkedin.com/in/ajaynaidu96/}{\underline{LinkedIn}} $|$
    \href{https://github.com/ajay-naidu-96/}{\underline{Github}} $|$
    \href{https://ajay-naidu-96.github.io/}{\underline{Portfolio}}
\end{center}

%-----------Objective-----------

\section{Objective}
Computer Vision Researcher with 5 years of experience delivering production-grade edge machine learning solutions at a
midsize B2B startup. Currently pursuing a research-focused M.S. in Artificial Intelligence at RIT, specializing in generative
vision models. My core interests lie in causal-representation learning, mechanistic interpretability, and efficient edge ML
systems. Actively seeking full time roles from Summer 2026.

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {\href{https://www.rit.edu/}{Rochester Institute of Technology (RIT)}}
    {Rochester, USA}
    {Master of Science in Artificial Intelligence (GPA: 3.96)}
    {Expected Aug. 2026}
  \resumeSubheading
    {\href{https://vtu.ac.in/en/}{Visvesvaraya Technological University (VTU)}}
    {Bangalore, India}
    {Bachelor of Engineering in Computer Science}
    {July 2018}
\resumeSubHeadingListEnd

  %-----------Technical SKILLS-----------
  \section{Technical Skills}
    \begin{itemize}[leftmargin=0.15in, label={}]
      \small{\item{
      \textbf{Operating System}{: ArchLinux, Ubuntu, Mac, Windows} \\
      \textbf{Languages}{: C++, Python, C} \\
      \textbf{Frameworks \& SDK}{: Pytorch, Keras, TensorRT, Deepstream, Flask, Pandas, Scikit, OpenCV, Git} \\
      \textbf{Certifications}{: Nvidia Jetson AI Specialist}
      }}
    \end{itemize}

%-----------EXPERIENCE-----------
\section{Research Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {\href{https://www.rit.edu/nrtai/}{AWARE-AI, RIT}}{Rochester, USA}
        {\textbf{NRT Trainee}, Advisor: Prof. Ferat Sahin}{Aug 2025 -- Present}  
    \resumeSubheading
        {\href{https://www.rit.edu/clasp/}{Computational Linguistics and Speech Processing Lab, RIT}}{Rochester, USA}
        {\textbf{Graduate Research Assistant}, Advisor: Prof. Cecilia Alm}{Aug 2025 -- Present}  
    \resumeSubheading
        {\href{https://www.rit.edu/cblwang/}{Computational Biomedicine Lab, RIT}}{Rochester, USA}
        {\textbf{Graduate Research Assistant}, Advisor: Prof. Linwei Wang}{Nov 2024 -- Present}  
          \resumeItemListStart
            \resumeItem{Conducting an independent study on evaluating existing Deep Causal Diffusion \& HVAE generative models on datasets known to exhibiting bias; Work under review, TPAMI, IEEE.}
            \resumeItem{Extending principles of Double ML techniques to GAN and Diffusion generative models.}
          \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://avathon.com}{Avathon}}{Austin, USA}
      {\textbf{AI Architect} $|$ DeepStream, Azure, C++, Python, TensorRT, Docker}{Aug 2019 -- Aug 2024}
      \resumeItemListStart
        \resumeItem{Founding engineer on the core Visual AI Advisor (VAIA) platform; played a crucial role scaling the company’s flagship
product from prototype to production, currently live across 1000+ client locations.}
        \resumeItem{Designed and deployed a stacked model inference strategy that improved object detection accuracy by 20\% for downstream
computer vision tasks for safety critical applications.}
        \resumeItem{Optimized computer vision models for both ARM-based and x86 architectures, improving perforformance and efficiency for
real-time edge computing applications.}
        \resumeItem{Implemented dynamic control logic for several downstream computer vision tasks, including HSE compliance monitoring,
footfall recognition, and fire detection.}
        \resumeItem{Led end-to-end delivery for multiple enterprise deployments, managing product timelines, customer requirements, and team
coordination.}
        \resumeItem{Led the implementation of vision analytics to recognize footfall patterns for the largest shopping mall chain in India,
achieving over 95\% accuracy.}
        \resumeItem{Developed vision AI solution to enhance surveillance capabilities for one of the world’s largest banks.}
        \resumeItem{Contributed to company’s growth through technical leadership, earning four promotions over five years.}
      \resumeItemListEnd

      \resumeSubheading
      {\href{https://www.entropik.io}{Entropik Tech}}{Bangalore, India}
      {\textbf{Computer Vision Intern} $|$ OpenCV, AWS, Python}{July 2018 -- Jan 2019}
      \resumeItemListStart
        \resumeItem{Contributed to their patented facial coding technology to recognize human emotions and human eye tracking.}
        \resumeItem{Automated facial action unit (AU) extraction using keypoints obtained from facial landmarks.}
        \resumeItem{Used support vector machine (SVM) algorithms to classifiy facial action units for human facial expression recognition.}
        \resumeItem{Introduced tracker based mechanism in the facial coding pipeline leading to reduced inference costs and sped-up the pipeline
by 50\%.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Academic Project}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Scene Flow Estimation of Autonomous Vehicles} $|$ \emph{Python, Keras, PCL}}{}
          \resumeItemListStart
            \resumeItem{Trained a regression neural network based off of VGG16 for scene flow estimation using 3D Point Clouds.}
            \resumeItem{Implemented custom data loaders for feeding inputs to the neural network in keras.}
            \resumeItem{Visualized the obtained point cloud data using point cloud library (PCL).}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------Relevant Coursework-----------
\section{Relevant Coursework}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
   Stanford 236 Deep Generative Models, Introduction to Causal Inference by Brady Neal, Causal Inference by Chandler Squires
(ongoing), EfficientML.ai (ongoing)
  }}
\end{itemize}
  

%
%-------------------------------------------
\end{document}