%-------------------------
% Resume in Latex
% Author : Ajay G
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Ajay Gopi} \\ \vspace{1pt}
    \small (+91) 897 128 3294 $|$ \href{mailto:ajaynaidu96@outlook.com}{\underline{ajaynaidu96@outlook.com}} $|$ 
    \href{https://www.linkedin.com/in/ajaynaidu96/}{\underline{linkedin.com/in/ajaynaidu96}} $|$
    \href{https://github.com/ajay-naidu-96/}{\underline{github.com/ajay-naidu-96}}
\end{center}

%-----------Professional Summary-----------
\section{Professional Summary}
AI professional with 5 years of industry experience, transitioning to academia to pursue advanced research in AI. Seeking to leverage industry insights and technical proficiency in AI / computer vision to contribute to cutting-edge research. Adept at bridging the gap between theoretical concepts and practical implementations, with a keen interest in pushing the boundaries of AI technology through research.

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Rochester Institute of Technology}{Rochester, USA}
    {Master of Science in Artificial Intelligence}{Aug 2024 -- Dec 2025(exp)}
  \resumeSubheading
    {SJB Institute of Technology}{Bangalore, India}
    {Bachelor of Engineering in Computer Science}{Aug 2014 -- July 2018}
    \resumeSubSubheading
      {Grade: First Class With Distinction}{Avg: 71.3\%}
\resumeSubHeadingListEnd

  %-----------Technical SKILLS-----------
  \section{Technical Skills}
    \begin{itemize}[leftmargin=0.15in, label={}]
      \small{\item{
      \textbf{Operating System}{: ArchLinux, Ubuntu, Windows} \\
      \textbf{Languages}{: C++, Python, C} \\
      \textbf{Frameworks \& SDK}{: Pytorch, Keras, TensorRT, Deepstream, Flask, Pandas, Scikit, OpenCV, Dlib} \\
      \textbf{Certifications}{: Nvidia Jetson AI Specialist}
      }}
    \end{itemize}

%-----------EXPERIENCE-----------
\section{Research Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Computation Biomedicine Lab, RIT}{Rochester, USA}
        {Graduate Research Assistant, Advisor: Prof. Linwei Wang}{Nov 2024 -- Present}  
          \begin{itemize}[leftmargin=0.15in, label={}]
            \small{\item{
              Research Interests: Few Shot Adaptation, Causal Inference, Representation Learning
            }}
          \end{itemize}
  \resumeSubHeadingListEnd

\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Avathon}{Bangalore, India}
      {AI Architect (VAIA Team)}{Dec 2021 -- Present}
      \resumeSubSubheading
        {AI Lead}{Jun 2021 -- Dec 2021}
      \resumeSubSubheading
        {Senior AI Engineer}{Jul 2020 -- Jun 2021}
      \resumeSubSubheading
        {AI Engineer}{Aug 2019 -- Jul 2020}
          \resumeItemListStart
            \resumeItem{Designed and built the computer vision inference pipeline, which is now used in over 1000+ banking and retail locations.}
            \resumeItem{Implemented an inference technique that improved the accuracy of the neural network model by more than 20\%.}
            \resumeItem{Was a key member of the Visual AI Advisor (VAIA) R\&D team responsible for improving the Vision AI inference pipeline as well as training and developing custom computer vision models.}
            \resumeItem{Delivered a solution that assisted in preventing theft from a banking institution, resulting in them saving assets worth several thousand dollars.}            
            \resumeItem{Was in charge of delivering vision analytics to recognize footfall patterns to the largest shopping mall chains in India at high accuracies (95+).}
            \resumeItem{Developed a Vision AI solution to aid surveillance at one of the world's largest banks and a Fortune 500 Company.}
            \resumeItem{Optimized neural networks for inferencing on ARM and x86 architectures.}
          \resumeItemListEnd

      \resumeSubheading
      {Entropik Tech}{Bangalore, India} 
      {Computer Vision Intern}{July 2018 -- Jan 2019}
      \resumeItemListStart
        \resumeItem{Contributed to their patented facial coding technology to recognize human emotions.}
        \resumeItem{Automated facial action unit (AU) extraction using keypoints obtained from facial landmarks.}
        \resumeItem{Used support vector machine (SVM) algorithms to classifiy facial action units for human facial expression recognition.}
        \resumeItem{Introduced tracker based mechanism in the facial coding pipeline leading to reduced inference costs and sped-up the pipeline by 50\%}
        \resumeItem{Performed statistical analysis on facial coding benchmark data and worked towards improving the eye tracking pipeline.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Academic Project}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Pose Estimation of Autonomous Vehicles} $|$ \emph{Python, Keras, PCL}}{}
          \resumeItemListStart
            \resumeItem{Trained a regression neural network based off of VGG16 for scene flow estimation using 3D Point Cloud Data.}
            \resumeItem{Wrote custom data loaders for feeding inputs to the neural network in keras.}
            \resumeItem{Visualized the obtained point cloud data using point cloud library (PCL).}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------Relevant Coursework-----------
\section{Relevant Coursework}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
   Stanford 236 Deep Generative Models, HTM Theory by Numenta, Linear Algebra by Gilbert Strang
  }}
\end{itemize}
  

%
%-------------------------------------------
\end{document}