\documentclass[letterpaper,9pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%-----------FONT OPTIONS----------
% sans-serif
\usepackage[sfdefault]{FiraSans}
% serif
%\usepackage{CormorantGaramond}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.25in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0.1in}

% Sections formatting
\titleformat{\section}[block]{\vspace{-5pt}\scshape\raggedright\large}{\thesection}{0.5em}{\titlerule \vspace{-5pt}}[\vspace{-5pt}]
\titleformat{\subsection}[block]{\vspace{-5pt}\scshape\raggedright\normalsize}{\thesubsection}{0.5em}{}[\vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, itemsep=-1pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Ajay Gopi} \\ \vspace{1pt}
    \small (+1) 585 498 8027 $|$ \href{mailto:ajaynaidu96@outlook.com}{\underline{ajaynaidu96@outlook.com}} $|$
    \href{https://www.linkedin.com/in/ajaynaidu96/}{\underline{linkedin.com/in/ajaynaidu96}}
\end{center}

%-----------Professional Summary-----------
\section{Professional Summary}
AI professional with 5 years of experience, transitioning to academia to pursue advanced research in AI. Skilled at applying theoretical AI and computer vision concepts to real-world solutions. Seeking to leverage industry experience to contribute to innovative research in AI.

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Rochester Institute of Technology}{Rochester, USA}
    {M.S. in Artificial Intelligence}{Aug 2024 -- Dec 2025(exp)}
  \resumeSubheading
    {SJB Institute of Technology}{Bangalore, India}
    {B.E. in Computer Science}{Aug 2014 -- Jul 2018}
    \resumeSubSubheading
      {Grade: First Class With Distinction}{Avg: 71.3\%}
\resumeSubHeadingListEnd

%-----------Technical SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{OS}{: ArchLinux, Ubuntu, Windows} \\
    \textbf{Languages}{: C++, Python, C} \\
    \textbf{Frameworks \& SDK}{: Pytorch, TensorRT, Deepstream, Flask} \\
    \textbf{Tools}{: Git, AWS, VS Code, Atom, LaTeX} \\
    \textbf{Libraries}{: Pandas, Scikit, OpenCV, Dlib, Numpy} \\
    \textbf{Certifications}{: Nvidia Jetson AI Specialist}
    }}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Research Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
        {Computation Biomedicine Lab, RIT}{Rochester, USA}
        {Graduate Research Assistant}{Nov 2024 -- Present}
          \begin{itemize}[leftmargin=0.15in, label={}]
            \small{\item{Research Interests: Few Shot Adaptation, Causal Inference, Representation Learning}}
          \end{itemize}
  \resumeSubHeadingListEnd

\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {SparkCognition}{Bangalore, India}
      {AI Architect (VAIA Team)}{Dec 2021 -- Aug 2024}
      \resumeSubSubheading
        {AI Lead}{Jun 2021 -- Dec 2021}
      \resumeSubSubheading
        {Senior AI Engineer}{Jul 2020 -- Jun 2021}
      \resumeSubSubheading
        {AI Engineer}{Aug 2019 -- Jul 2020}
          \resumeItemListStart
            \resumeItem{Built computer vision inference pipeline used in 1000+ retail/banking locations.}
            \resumeItem{Improved neural network accuracy by 20\%.}
            \resumeItem{Improved Vision AI models for retail and surveillance applications.}
            \resumeItem{Helped prevent theft in banking, saving significant assets.}
            \resumeItem{Led footfall recognition project for large shopping malls with 95+% accuracy.}
            \resumeItem{Optimized neural networks for ARM and x86 architectures.}
          \resumeItemListEnd

      \resumeSubheading
      {Entropik Tech}{Bangalore, India}
      {Computer Vision Intern}{Jul 2018 -- Jan 2019}
      \resumeItemListStart
        \resumeItem{Contributed to patented facial coding technology for emotion recognition.}
        \resumeItem{Optimized facial action unit extraction and sped up pipeline by 50\%.}
        \resumeItem{Improved eye tracking pipeline and automated facial expression recognition.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Academic Project}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Pose Estimation of Autonomous Vehicles} $|$ \emph{Python, Keras, PCL}}{}
          \resumeItemListStart
            \resumeItem{Trained regression neural network based on VGG16 for scene flow estimation.}
            \resumeItem{Created custom data loaders and visualized point cloud data using PCL.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\end{document}
